%
% Einstein Platform User’s Manual (Beta)
%
% Code source LaTeX2e.
%
% Requiert un certain nombre de paquets (fournis avec la distribution de 
% i-Packages et sans doute la plupart des distributions):
% - palatino
% - hyperref
%
\documentclass[a4paper, english, 11pt]{article}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{palatino}
\usepackage[applemac]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[top=2cm,bottom=2cm,left=1.5cm,right=1.5cm]{geometry}
\usepackage[
	bookmarksopen=true,
	pdfstartview=,
	pdftitle=Einstein\ Platform\ User’s\ Manual,
	pdfauthor=Paul\ Guyot,
	pdfborder=false]{hyperref}
\title{\Huge Einstein Platform\\
User’s Manual\\
 \\
\small{For Einstein Platform Beta}}
\begin{document}
% Paramètres pour le document:
% ajustage de l'espace entre les caractères pour la justification
\setlength{\emergencystretch}{12em}
% macro pour insérer une URL
\def\url#1{\href{#1}{\underline {\tt {#1}}}}
\maketitle
%
\newpage
\tableofcontents
\newpage
% espace entre les paragraphes
\parskip = 0.2in
\parindent = 0.0in
\pagestyle{myheadings}
\markright{Einstein Platform User’s Manual}
\section{Introduction}
Einstein Platform is a way to transform a PDA in a next-generation Newton N2
(MP2x00, eMate 300).

Einstein Platform is the successor of Einstein Emulator and it has been unveiled at
the Worldwide Newton Conference 2006:
\url{http://wwnc.newtontalk.net/}

\newpage
\section{Requirements}

To run Einstein Platform, you will need:
\begin{itemize}
\item an arm-linux PDA with X11, 2.3.3 libc with soft FPU and enough memory.
\item a NewtonOS 2.1 ROM
\item a compact flash card with at least 40 MB free.
\end{itemize}

\begin{itemize}
\item Einstein Platform requires an MP2x00 US, an MP2x00 D or an eMate 300 ROM image.
\end{itemize}

Instructions about how to extract the ROM are available in Einstein Emulator's
documentation. Einstein Emulator can be used to extract the ROM on MacOS X.

http://www.kallisys.com/files/newton/Einstein/UserManual-UP2.pdf

I used a Zaurus SL-5500 (thanks Sylvain) with OpenZaurus (http://www.openzaurus.org/) 3.5.4-rc
ROM and the following packages:

\begin{itemize}
\item \verb|libstdc++6_3.4.3-r10_arm.ipk|
\item \verb|libts-0.0-0_0.0cvs20050403-r18_arm.ipk|
\item \verb|libx11-6_6.2.1-r2_arm.ipk|
\item \verb|libxau0_0.1.1-r1_arm.ipk|
\item \verb|libxcalibrate0_0.0cvs20050403-r0_arm.ipk|
\item \verb|libxdmcp0_0.1.3-r1_arm.ipk|
\item \verb|libxext6_0.0cvs20050222-r1_arm.ipk|
\item \verb|libxfont1_1.4.2-r2_arm.ipk|
\item \verb|libxft2_2.1.6-r1_arm.ipk|
\item \verb|libxrandr2_1.0.2-r1_arm.ipk|
\item \verb|libxrender1_0.8.4-r1_arm.ipk|
\item \verb|tslib-conf_0.0cvs20050403-r18_collie.ipk|
\item \verb|ttf-bitstream-vera_1.10-r2_all.ipk|
\item \verb|xserver-kdrive-fbdev_20050207-r0_arm.ipk|
\item \verb|xtscal_0.6.3-r0_arm.ipk|
\end{itemize}

\newpage
\section{Starting Einstein Platform}

\begin{itemize}
\item Name the ROM dump either:
717006 (MP2x00 US)
737041 (MP2100 D)
747129 (eMate 300)

\item Put the file on the compact flash, next to Einstein.rex file.

\item Run the X server. Xfbdev on the Zaurus needs to be run at 270 degrees:
\verb|Xfbdev -screen 320x240@270 -dpi 100 &|

\item Run the X server and then Einstein Platform with:\\
\verb|/mnt/cf/einstein --machine=XXXX --width=YYYY --height=ZZZZ /mnt/cf|
\end{itemize}

where XXXX should be either:
717006 (for a MP2x00 US)
737041 (for a MP2100 D)
747129 (for an eMate 300)

and YYYY and ZZZZ should be set properly.

\subsection{Options}
\verb|./einstein --help| will print some help about the options. The options are summarized below:

\verb|--audio| or \verb|-a|\\
Select the audio driver. Choose null to disable sound, sound doesn't work yet.

\verb|--screen| or \verb|-s|\\
This option is useless now as the only available screen driver is x11. Framebuffer support may be added later.

\verb|--width|\\
Set the width of the screen (in portrait mode). Default is 320.

\verb|--height|\\
Set the height of the screen (in portrait mode). Default is 480.

\verb|--log| or \verb|-l|\\
Set the log file. Default is to not log. This option is incompatible with --monitor.

\verb|--restore| or \verb|-r|\\
This option is unimplemented.

\verb|--machine| or \verb|-m|\\
Set the machine. Choose 717006 for a MP2x00 US, 737041 for a MP2100D or 747129 for an eMate 300. \verb|--machine| option can be omitted with a 717006 ROM file.

\verb|--monitor|\\
Run in monitor mode.

\verb|--ram|\\
Set the RAM size in 64 KB increment. 1 will mean 64 KB of RAM. 64 is the default setting (4 MB). The maximum is 255 (nearly 16 MB).

\subsection{Commands}

Using the cli flavor, you will be provided with a prompt. Typing help will provide a small help about the available commands. This only works if you can access the console, of course.

\newpage
\section{Known problems}

\begin{itemize}
\item Serial ports are not emulated.
\item PCMCIA cards are not emulated. The sockets aren’t entirely emulated yet.
\item The sound volume is reported to be settable by software but the changes are ignored (except when the sound is off on the Newton).
\item Sound input isn't emulated.
\item An error occurs when trying to install system patches.
\item Keys are not translated properly (the keyboard is useless).
\item Rotation doesn't work well.
\item It is awfully slow.
\end{itemize}

Please drop me a line (\url{mailto:pguyot@kallisys.net}) if you experience a problem which is not in this list.

\newpage
\section{Changes History}

1/14/06 Einstein Platform Beta
\begin{itemize}
\item Initial release.
\end{itemize}

\newpage
\section{License}

Einstein Platform is copyright 2005-2006 by Paul Guyot.
It is provided as is, without any warranty of any kind.

Einstein Platform includes portaudio v19 (from CVS).

\begin{verbatim}
/*
 * PortAudio Portable Real-Time Audio Library
 * Latest Version at: http://www.portaudio.com/
 *
 * Copyright (c) 1999-2000 Phil Burk and Ross Bencina
 *
 * Permission is hereby granted, free of charge, to any person obtaining
 * a copy of this software and associated documentation files
 * (the "Software"), to deal in the Software without restriction,
 * including without limitation the rights to use, copy, modify, merge,
 * publish, distribute, sublicense, and/or sell copies of the Software,
 * and to permit persons to whom the Software is furnished to do so,
 * subject to the following conditions:
 *
 * The above copyright notice and this permission notice shall be
 * included in all copies or substantial portions of the Software.
 *
 * Any person wishing to distribute modifications to the Software is
 * requested to send the modifications to the original developer so that
 * they can be incorporated into the canonical version.
 *
 * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
 * EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
 * MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
 * IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR
 * ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF
 * CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION
 * WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
 *
 */
\end{verbatim}

Einstein Platform also includes NetBSD arm disassembler.

\begin{verbatim}
// $NetBSD: disassem.c,v 1.14 2003/03/27 16:58:36 mycroft Exp $
//
// Copyright (c) 1996 Mark Brinicombe.
// Copyright (c) 1996 Brini.
//
// All rights reserved.
//
// Redistribution and use in source and binary forms, with or without
// modification, are permitted provided that the following conditions
// are met:
// 1. Redistributions of source code must retain the above copyright
//    notice, this list of conditions and the following disclaimer.
// 2. Redistributions in binary form must reproduce the above copyright
//    notice, this list of conditions and the following disclaimer in the
//    documentation and/or other materials provided with the distribution.
// 3. All advertising materials mentioning features or use of this software
//    must display the following acknowledgement:
//	This product includes software developed by Brini.
// 4. The name of the company nor the name of the author may be used to
//    endorse or promote products derived from this software without specific
//    prior written permission.
//
// THIS SOFTWARE IS PROVIDED BY BRINI ``AS IS'' AND ANY EXPRESS OR IMPLIED
// WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
// MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED.
// IN NO EVENT SHALL BRINI OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT,
// INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
// (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
// SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
// HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, 
// STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN
// ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE
// POSSIBILITY OF SUCH DAMAGE.
\end{verbatim}

\end{document}
